Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
minor raising degree theorem wording edits

We next show $y_{i, e_i}$ also satisfies the second part of the
claim of $(a),$ by considering separately the cases of whether $j
\in S(i,0),$ and $j \notin S(i,0)$.

@@

To show (c), we wish to show $y_{i, e_i}z \in R'$ for $z \neq y_{i, e_
i}, y_{i, e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}

\noindent
We now check this in three cases, depending on whether $j \notin \{
i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.

>>>>

We next show $y_{i, e_i}$ also satisfies the second part of the
claim of $(a),$ by considering separately the cases of whether $j
\in S(i, 0),$ and $j \notin S(i,0)$.

@@

To show (c), we wish to show that $f := y_{i, e_i}z \in R'$ for $z
\neq y_{i, e_i} \text{ or } y_{i, e_i'}$. Note that $f \in R$ lies
in $R'$ if and only if for all $j \in J$ we have
\begin{align*}
	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
\end{align*}

\noindent
We now check this in three cases, depending on whether $j \notin \{
i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
